Spfy: an integrated graph database for real-time prediction of Escherichia coli phenotypes and downstream comparative analyses

### 2018-04-02 paper-webserver.tex
EDIT: note that bap uses https://en.wikipedia.org/wiki/TORQUE
ADD: some specs on bap timings

Spfy is similar to these technologies in that it automates workflows for users, and as in Galaxy, uses task queues to distribute selected analyses.
% re: Matt "2. When comparing to IRIDA, BAP etc., can mention some differences with Superphy, e.g. the storage of interim result data that allows downstream integrated analysis"

% If we mention speed comparisons, we need to have actual data supporting them
On a per file basis, Spfy performs at a similar speed to BAP on predictive genomics tasks, usually completing within 2-3 minutes, though Spfy does not provide genome assembly services.
However, unlike these workflow managers, Spfy is designed to help solve the needless re-computation of analyses by storing results in a graph database for downstream comparative studies. This allows Spfy to perform population-wide analyses, regardless of the individual software used to generate the results for a given genome.

>>>>

Spfy is similar to these technologies in that it automates workflows for users and uses task queues to distribute selected analyses.
% re: Matt "2. When comparing to IRIDA, BAP etc., can mention some differences with Superphy, e.g. the storage of interim result data that allows downstream integrated analysis"

% If we mention speed comparisons, we need to have actual data supporting them
On a per file basis, Spfy performs at a similar speed to BAP on predictive genomics tasks, though Spfy does not provide genome assembly services.
After accounting for assembly services, BAP reported \cite{thomsen2016bacterial} an average runtime of 8-9 minutes per genome over 476 runs.
ResFinder, which is similar to the RGI program used by Spfy, took an average of 3-4 minutes.
However, unlike these workflow managers, Spfy is designed to help solve the needless re-computation of analyses by storing results in a graph database for downstream comparative studies. This allows Spfy to perform population-wide analyses, regardless of the individual software used to generate the results for a given genome.
